\pkg{cleanR}: Your Personal Maid for Cleaning Datasets in \proglang{R}

### 2016-10-10 latex/article.Rnw
Rnw-fix

\section{Introduction}
Statisticians and data analysts spend a large portion of their time on
data cleaning and on data wrangling. Packages such as \pkg{data.table}, \pkg{plyr},
and \pkg{} make data wrangling a lot easier in R, but there are only a
few options available for automated data cleaning.

>>>>

\section{Introduction}
Statisticians and data analysts spend a large portion of their time on
data cleaning and on data wrangling. Packages such as
\pkg{data.table}, and \pkg{plyr} have made data wrangling a lot easier in
\proglang{R}, but there are only a few options available for automated data
cleaning.
